### 2024-10-16 teaching/math240f24/draft.tex
Constance Rooke

Let's see how to use this theorem. Suppose we want to know if the number $\root 6\of 18$ is
irrational or not. Well, since $1^6 = 1$ and $2^6 = 64$, we have $1^6 < 18 < 2^6$,
meaning that $1<\root 6\of 18 < 2$. (This is because the function $f:\RR\to\RR$ defined
by $f(x) = x^6$ is increasing on the interval $[1,2]$.) Hence $\root 6\of 18$ is not
an integer, and by the theorem it must be irrational.

>>>>

Let's see how to use this theorem. Suppose we want to know if the number $\root 6\of{18}$ is
irrational or not. Well, since $1^6 = 1$ and $2^6 = 64$, we have $1^6 < 18 < 2^6$,
meaning that $1<\root 6\of{18} < 2$. (This is because the function $f:\RR\to\RR$ defined
by $f(x) = x^6$ is increasing on the interval $[1,2]$.) Hence $\root 6\of{18}$ is not
an integer, and by the theorem it must be irrational.
